---
title: "Assignment 3"
author: "Sydney Berman"
date: "January 26, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

## Project Info
Date: January 26, 2020
Link to git repository: https://github.com/sydberman/BIOL432.git 

```{r data setup}
getwd()
MyData<-read.csv("InputData/FallopiaData.csv",header=T)
summary(MyData) #check the data 
head(MyData)

```

Use filter to remove any rows with ‘Total’ biomass < 60 
```{r}
MyData1<-filter(MyData,Total<60)
head(MyData1) #check the data 
```

Reorder the columns so that they are in the order: ‘Total’, ‘Taxon’, ‘Scenario’, ‘Nutrients’, and remove the other columns
```{r reordering columns}
col_order<- c("Total", "Taxon", "Scenario", "Nutrients") #List of column order 
MyData2<- MyData1[, col_order] #indexing new columns
head(MyData2) #checking new column order 
```

Make a new column TotalG, which converts the ‘Total’ column from mg to grams AND replace Total with TotalG.
```{r}
MyData3<- transmute(MyData2, TotalG=Total/1000,Taxon, Scenario,Nutrients) #changing and replacing Total column, including other columns wanting to include 
head(MyData3) #check new column is replaced properly 
```

## Custom Function 
Write a custom function that will take two inputs from the user: 1. a vector of data to process (e.g. column from a data.frame object) and 2. a string that defines what calculation to perform.
```{r}
functionName<-function(column,command){
  if (command=="Average") {
    column <- enquo(column) #allows column name to be used in the function 
    print(MyData3%>%group_by(Nutrients) %>%summarize(Mean=mean(!!column))) #group by nutrient level and gets mean for column 
  }
  else if (command=="Sum"){ #sums the column given
    print(sum(column))
  }
  else if (command=="Observations"){
    column <- enquo(column)#allows column name to be used in the function 
    print(MyData3%>%group_by(!!column)%>%summarize(n=n())) #counts the number of observations in the column
  }
  else{
    print("error") #prints error if anything other than 3 commands 
    }
}

```

Check to ensure function works properly 
```{r}
functionName(MyData3$TotalG,"Sum") #expect the sum of TotalG column
functionName(fun, "hello") #expect an error

```
Write some R code that uses your function to count the total number of observations in the 'Taxon' column.
```{r}
functionName(Taxon,"Observations")
```
Write some R code that uses your function  to calculate the average TotalG for each of the two Nutrient concentrations.
```{r}
functionName(TotalG,"Average")
```

Write (i.e. save) the new data to a file called "WrangledData.csv" in the Output folder.
```{r}
write.csv(MyData3,"Output/WrangledData.csv")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
