---
title: "Assignment 4"
author: "Sydney Berman"
date: "February 2, 2021"
output: html_document
---
## Project Info
Date: February 2, 2020
Link to git repository: https://github.com/sydberman/Assignment3

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

##Setup 
Create a new R Markdown file called Regex.Rmd and add code for each of the following steps:
Import your measurements.csv file from the Week 1 Assignment into an object called MData
```{r cars}
MData<-read.csv("measurements.csv",header=T) #import data set 

#check data 
head(MData)

```

Use a dplyr command AND regular expression(s) to add a new column called Sp that shortens the genus name in the Organism column to only the first letter and period
```{r}
dat<-mutate(MData, Sp=gsub("(^\\w)(\\w+)\\s(\\w+)","\\1. \\3",MData$Organism)) #anything with 2 words will be substituted to have the first word shortened to only the first letter, followed by a period, space and the second word
print(dat)

```

Use a dplyr command to create a new dataset BUT with Sp column instead of the Organism column, moved to the beginning in place of the original Organism column.
```{r}
dat<-select(dat, Sp, Limb.width:Observer) #since the new data is created can selec and rearrange for columns wanted 
head(dat) #check data 

```

Save the dataset as a new file called MeasShort.csv
```{r pressure, echo=FALSE}
write.csv(dat,"MeaShort.csv") #saves new file 
```

Commit these changes using Git in RStudio
